---
title: "PSYC501_Lab#11_RMD"
author: "Qianhui Ni"
date: "11/22/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval = TRUE)
```
&nbsp;  

# Introduction

**This is Qianhui's assignment for PSYC501 Lab Section #11.**  
Name: **Qianhui Ni**  
Lab Section Number:**52662**  
USC Student ID:**00000000000**  
  
# Excercises  
## Exercise 1. Symmetric Bootstrap-t with Trimmed Means  
 
```{r E1}
library(psych)
library(WRS)
#Step1 
lab11b <- read.table(file="lab11b.txt")
lab11b <- unlist(lab11b)
#Step2 
xbart <- tmean(lab11b)
xbart
#Step3 
resample <- function(data , sam_size , num_sam) {
  mat <- matrix(nrow = sam_size , ncol = num_sam)
  for(i in 1:num_sam) {
    mat[ , i] <- sample(data , sam_size , replace = TRUE)
  }
  mat <- matrix(mat , nrow = sam_size , ncol = num_sam)
}

M1 <- resample(lab11b, length(lab11b) , 2000)
#Step4
results.11b <- apply(M1 , 2 , trimci , null.value = xbart , pr = F)
#Step5
stats.11b <- lapply(results.11b , "[[" , "test.stat")
stats.11b <- unlist(stats.11b)
head(stats.11b)
class(stats.11b)
#Step6
stats.11b2 <- abs(stats.11b)
#Step7
t_stats <- sort(stats.11b2)
```
Step 8: In this step, we will make a statistical decision. 
Method 1: Using the critical test statistic.
```{r E1S8M1}
c <- (1-0.05) * 2000
Tstar <- t_stats[c]
Tt <- abs((1 / trimse(lab11b)) * xbart)
Tstar < Tt
```
## The value for T*t(c) is `r Tstar`.    

## Because Tt is larger that Tstar, we reject the null hypothesis.  
&nbsp;  
Method 2: Using the confidence interval for symmetric bootstrap-t.  
```{r E1S8M2}
CI_down <- xbart - Tstar*trimse(lab11b)
CI_up <- xbart + Tstar*trimse(lab11b)
0 > CI_down
0 < CI_up
```
## Ans: The CI is (`r CI_down`,`r CI_up`).
## The null value is not within the CI, so we reject the null hypothesis.  
&nbsp;  
Of course, we can use the function trimcibt() to do this conveniently. Does the result resemble that you obtained earlier?   
```{r E1S8M21}
trimcibt(lab11b, tr=0.2, alpha=0.05, nboot=2000, side=TRUE)
```
## The null value is within the CI so we cannot reject the null hypothesis. The result does not resemble the earlier one.
&nbsp;  

## Exercise 2. Bootstrap method for non-linear associations
```{r E2}
lab11c <- read.table(file="lab11c.txt")
plot(lab11c$v1, lab11c$v2, main="Scatterplot",
   xlab="V1 ", ylab="V2 ")
cor.test(lab11c$v1, lab11c$v2)
indt(lab11c$v1, lab11c$v2) 
```
## Ans: As it can be seen from the scatterplot, The association between V1 and V2 is not linear. When V1 < 0, V2 is related to V1 negatively. But when V1 > 0, the pattern totally changed. This curvature affects the magnitude of Pearson’s correlation. So when using Pearson's product-moment correlation we cannot find a significant association. While indt() is based on the wild bootstrap method and this method is sensitive to any curvature. So when using indt() we can find a significant association. 
\pagebreak  
