---
title: "PSYC501_Lab#2_RMD"
author: "Qianhui Ni"
date: "9/11/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval = TRUE)
```
&nbsp;  

# Introduction

**This is Qianhui's assignment for PSYC501 Lab Section #2.**  
Name: **Qianhui Ni**  
Lab Section Number:**52662**  
USC Student ID:**0000000000**  
&nbsp;  
  
# Excercises

## Excercise 1  
a). Generate ONE random value from a normal distribution with mean=5 and sd=2, and save it to an object named x.  
b). Use pnorm(?, 5, 2) to find the probability p(X <= x)  
c). Use qnorm(?, 0, 1) to find the standard normal quantile corresponding to the probability obtained in (b).  
d). Use arithmetic operations in R to standardize the value x you generated in (a).  
e). Is your answer in (c) same as that in (d)?  
&nbsp;  

### Excercise 1. a):
```{r E1a}
x <- rnorm(1,5,2)
x
```
### Excercise 1. b):
```{r E1b}
e1_p <- pnorm(x, 5, 2)
e1_p
```
### Excercise 1. c):
```{r E1c}
e1_q <- qnorm(e1_p, 0, 1)
e1_q
```
### Excercise 1. d):
```{r E1d}
e1_sd_x <- (x-5)/2
e1_sd_x
```
### Excercise 1. e):
```{r E1e}
e1_q == e1_sd_x
```
**Ans: Yes, they are the same.**  
&nbsp;  
\newpage  

## Excercise 2  
a). Download lab2.csv and import it as a table object named lab2.  
b). Create a histogram for the reaction time (rt) data. To make your graph look more nuanced, play with the parameter br= to change the number of bins shown.  
c). Is this set of data skewed? Positively or negatively?  
d). Calculate the mean, median, and variance. Which statistic is larger: the mean or the median?  
e). Draw two vertical lines: one to indicate where the mean is located and the other to indicate where the median is located. Use this function: abline(v=?).  
&nbsp;  

### Excercise 2. a):
```{r E2a}
setwd("/Users/qianhuini/Documents")
e2_Data <- read.csv(file="lab2.csv", header=TRUE,sep = "")
```
### Excercise 2. b):
```{r E2b}
hist(e2_Data$rt, br = 100)
```

### Excercise 2. c):
```{r E2c}
library(moments)
e2_skew <- skewness(e2_Data$rt)
if (e2_skew[1] > 0){
  print("The data is skewed positively")
} else if (e2_skew[1] <0){
  print("The data is skewed negatively")
} else {
  print("The data is not skewed")
}
```
**Ans: The skewness of the simulated data is `r e2_skew[1]`. This concludes that the rt is shewed positively.**  

### Excercise 2. d):
```{r E2d}
e2_mean <- mean(e2_Data$rt)
e2_median <- median(e2_Data$rt)
e2_variance <- var(e2_Data$rt)
if (e2_mean > e2_median){
  print("its mean is larger than itsmedian")
} else if (e2_mean < e2_median){
  print("its median is larger than its mean")
} else {
  print("its mean and median are the same")
}
```
**Ans: Its mean is larger than itsmedian.**  

### Excercise 2. e):
```{r E2e}
{hist(e2_Data$rt, br = 100)
abline(v=e2_mean, col="red")
abline(v=e2_median,col="blue")}
```
&nbsp;  

## Excercise 3  
a). Generate 50 values from a standard normal distribution and store them in a vector X1.
b). Generate 50 values from a normal distribution with mean=0 & sd=20. Store them in a vector X2. 
c). Combine the two vectors to form a new vector X. [hint: use the function c(...)]
d). Plot the data in X using the function hist(X).
e). Calculate the mean, median, variance and standard deviation of the data in X.
f). Plot density graphs for the three distributions you generated in this exercise in one window.
&nbsp;  

### Excercise 3. a),b),c):
```{r E3abc}
X1 <- rnorm(50,0,1)
X2 <- rnorm(50,0,20)
X <- c(X1,X2)
```
### Excercise 3. d):
```{r E3d}
hist(X)
```

### Excercise 3. e):
```{r E3e}
e3_mean <- mean(X)
e3_median <- median(X)
e3_sd <- sd(X)
```
**Ans: For the data in X, its mean is `r e3_mean`, its median is `r e3_median`, its sd is `r e3_sd`.**   
\newpage

### Excercise 3. f):
```{r E3f}
par(mfrow=c(1,3))
hist(X1,br=10,col="coral2")
hist(X2,br=10,col="lightskyblue2")
hist(X,br=10,col = "mediumpurple2")
```
