---
title: "PSYC501_Lab#4_RMD"
author: "Qianhui Ni"
date: "10/05/2019"
output:
  pdf_document: default
  html_document:
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE,eval = TRUE)
```
&nbsp;  

# Introduction

**This is Qianhui's assignment for PSYC501 Lab Section #4.**  
Name: **Qianhui Ni**  
Lab Section Number:**52662**  
USC Student ID:**000000001**  
  
&nbsp;  

# Writing My Functions  
For this assignment, I would like you to write your own R functions to calculate:  
1)	The mean  
2)	The trimmed mean  
3)	The median   
&nbsp;  

## 1). The mean  
```{r E4mean}
my.mean = function(x){
  n <- length(x)
  mean <- sum(x)/n
  return(mean)
}
```
&nbsp;  

## 2). The median    
```{r E4median}
my.median = function(y){
  n <- length(y)
  sorted_y <- sort(y)
  remainder <- n %% 2
  if(remainder == 1){
    median <- sorted_y[(n+1)/2]
  }
  else{
    m1 <- sorted_y[n/2] + sorted_y[(n/2)+1]
    median <- m1/2
  }
  return(median)
}
```
&nbsp;  

## 2). The trimmed mean    
```{r E4tmean}
my.tmean = function(z,trim = 0.2){
  if( (trim<0) | (trim>=0.5) ){
    tmean <- "Incorrect input! The value must be between 0 and 0.5."
  }
  else{
    n <- length(z)
    sorted_z <- sort(z)
    g <- floor(trim*n)
    location <- vector()
    if(g!=0){
      for(i in 1:n){
        if( (i<=g) | (i>(n-g)) ){
          location <- c(location,i)
        }
      }
      new_z <- sorted_z[-location]
      new_n <- length(new_z)
      tmean <- sum(new_z)/new_n
    }
    else{
      tmean <- sum(z)/n
    }
  }
  return(tmean)
}
```
&nbsp;  
&nbsp;  

# Test of  My Functions  
```{r lib, include=FALSE}
library(WRS)
```
## Generate Test Samples  
```{r testexample}
test1 <- rnorm(100)
test2 <- rnorm(101)
```
## Test of my.mean  
```{r t1}
my.mean(test1)
mean(test1)
my.mean(test2)
mean(test2)
my.mean(test1) == mean(test1)
my.mean(test2) == mean(test2)
```

## Test of my.median  
```{r t2}
my.median(test1)
median(test1)
my.median(test2)
median(test2)
my.median(test1) == median(test1)
my.median(test2) == median(test2)
```


## Test of my.tmean 
```{r t3}
my.tmean(test1,0.2)
tmean(test1,0.2)
my.tmean(test2,0.1)
tmean(test2,0.1)
my.tmean(test1,0.2) == tmean(test1,0.2)
my.tmean(test2,0.1) == tmean(test2,0.1)
```

&nbsp;  
&nbsp;  